Title

### 2012-09-05 inc/plasmon/plasmon.tex
remove some unicode

Every material has an intrinsic plasma frequency given by 
\begin{equation}
  \omega_{P} = \sqrt{\frac{n e^2}{\varepsilon_{0} m^*}}
\end{equation}
where $n$ is the electron density and $m*$ is the effective mass of the material.
In order to drive a plasmon on the surface of a material, the portion of the laser wave-vector parallel to the plasmon ($\vec{k}_{laser,x}$) must be matched to the wave-vector of the surface plasmon.

>>>>

Every material has an intrinsic plasma frequency given by 
\begin{equation}
  \omega_{P} = \sqrt{\frac{n e^2}{\varepsilon_{0} m^*}}
\end{equation}
where $n$ is the electron density and $m*$ is the effective mass of the material.
In order to drive a plasmon on the surface of a material, the portion of the laser wave-vector parallel to the plasmon ($k_{Lx}$) must be matched to the wave-vector of the surface plasmon.
\begin{equation}
  k_{P} = k_{Lx} + i k_{G}
\end{equation}
